### 2014-03-20 paper/introduction.tex
integrate new temp figure

The generation of these pipes, however, is not trivial.  Pipes need to be as straight as possible to ease the insertion of media post-print.  Independent pipes should not intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface (unless they are being used for display purposes), especially since consumer-grade 3D printers do not guarantee air- or water-tightness of their prints, so more than one layer may be required to prevent leakage.

>>>>

The generation of these pipes, however, is not trivial.  Pipes need to be as straight as possible to ease the insertion of media post-print.  Independent pipes should not intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface (unless they are being used for display purposes).  Consumer-grade 3D printers do not guarantee air- or water-tightness of their prints, so more than one layer may be required to prevent leakage.  Finally, pipes
